Notes: New gaugings in 3d from three-form

### 2022-06-24 Notes_3dH3.tex
Sections on 6d (1,0), (2,0) and (1,1), and schematic results for IIA.

\section{\texorpdfstring{${\rm AdS}_{3}\times S^{3}$}{AdS3xS3}: a proof of concept}
We start by reproducing the analysis of ref.~\cite{Eloy:2021fhc} to prove the validity of our method. We consider reductions within the minimal ${\cal N}=(1,0)$ six-dimensional supergravity, leading to duality group $\SO(4,4)$ in three dimensions, from which the half-maximal cases ${\cal N}=(1,1)$ and ${\cal N}=(2,0)$ can be deduced (in those cases the duality group in three dimensions in $\SO(8,4)$).

The coordinates $X^{[MN]}$ of the $\SO(p,q)$ exceptional field theory of ref.~\cite{Hohm:2017wtr} sit in the adjoint $\bm{28}$ of $\SO(4,4)$. Under $\SO(4,4)\rightarrow\SO(3,3)\times\R_{+}$, it decomposes into
\begin{equation}
  \begin{aligned}
    \bm{28} &\longrightarrow \bm{6}_{2} \oplus \bm{1}_{0} \oplus \bm{15}_{0} \oplus \bm{6}_{-2},\\
    X^{MN} &\longrightarrow \{Y^{A0},Y^{0}{}_{0},Y^{[AB]},Y^{A}{}_{0}\}.
  \end{aligned}
\end{equation}
Further decomposing $\SO(4,4)\rightarrow\SO(3,3)\times\R_{+}\rightarrow\SL(3)\times\R_{+}\times\R_{+}$, we get
\begin{equation}
  \bm{28} \longrightarrow \left[\bm{\bar{3}}_{2,2} \oplus \bm{3}_{-2,2}\right] \oplus \bm{1}_{0,0} \oplus \left[\bm{3}_{4,0} \oplus \bm{1}_{0,0} \oplus \bm{8}_{0,0} \oplus \bm{\bar{3}}_{-4,0}\right] \oplus \left[\bm{\bar{3}}_{2,-2} \oplus \bm{3}_{-2,-2}\right].
\end{equation}
They are two physically different possibilities to embed the internal coordinates in $X^{MN}$, corresponding to the two different half-maximal supergravities in six dimensions:\footnote{The choices are equivalent in $\SO(4,4)$ (through triality), but different once embedded in $\SO(8,4)$.}
\begin{equation}
  \begin{aligned}
    {\cal N}=(1,1):&\qquad y^{m}=Y^{m0}\quad {\rm in}\quad  \bm{\bar{3}}_{2,2} \subset \bm{6}_{2},\\
    {\cal N}=(2,0):&\qquad \tilde{y}_{m}=\varepsilon_{mnp}Y^{np}\quad {\rm in}\quad  \bm{3}_{4,0} \subset \bm{15}_{0}.
  \end{aligned}
\end{equation}

@@

\paragraph{\boldmath $H_{(7)}^{\alpha}$ and $H_{(5)}$ in $\SL(8)_{\rm IIB}$} Now that we know what are the $\SL(8)_{\rm IIB}\times\R_{+}$ representations corresponding to the internal coordinates, $C_{(6)}^{\alpha}$ and $C_{(4)}$, we can infer those of $H_{(7)}^{\alpha}$ and $H_{(5)}$:
\begin{equation}  \label{eq:H7H5inIIB}
  \begin{aligned}
    H_{(7)}^{\alpha} & \subset \bm{\bar{28}}_{2} \otimes \left(\bm{8}_{3}\oplus\bm{63}_{0}\right) = \bm{\bar{8}}_{5} \oplus \bm{\bar{216}}_{5} \oplus \bm{\bar{28}}_{2} \oplus \bm{\bar{36}}_{2} \oplus \bm{\bar{420}}_{2} \oplus \bm{\bar{1280}}_{2}, \\
    H_{(5)} & \subset \bm{\bar{28}}_{2} \otimes \bm{56}_{1} = \bm{8}_{3} \oplus \bm{216}_{3} \oplus \bm{1344}_{3}.
  \end{aligned}
\end{equation}

@@

>>>>

\section{\texorpdfstring{${\rm AdS}_{3}\times S^{3}$}{AdS3xS3}: a proof of concept}
We start by reproducing the analysis of ref.~\cite{Eloy:2021fhc} to prove the validity of our method. They are two different half-maximal supergravities in six dimensions, with ${\cal N}=(2,0)$ and ${\cal N}=(1,1)$. They both admit consistent truncation on $S^{3}$~\cite{Hohm:2017wtr,Samtleben:2019zrh}, leading to half-maximal gauged supergravity in three dimensions with duality group $\SO(8,4)$. These truncations have isometry group $\SO(4)\times\SO(4)$ and are constructed in terms of two different $\SO(3,3)$ subgroups of $\SO(8,4)$:
\begin{subequations}
  \begin{align}
    {\cal N}=(2,0):&\qquad \SO(8,4)\longrightarrow\SO(3,3)_{(2,0)}\times \SO(5,1)\longrightarrow\SO(3,3)_{(2,0)}\times \SO(5), \label{eq:SO84decomp20}\\
    {\cal N}=(1,1):&\qquad \SO(8,4)\longrightarrow\SO(4,4)\times \SO(4)\longrightarrow\SO(3,3)_{(1,1)}\times\R_{+}\times\SO(4). \label{eq:SO84decomp11}
  \end{align}
\end{subequations}

  \subsection{\texorpdfstring{${\cal N}=(2,0)$}{N=(2,0)} six-dimensional supergravity}

  \paragraph{6d origin of the three-forms} The ${\cal N}=(2,0)$ supergravity features 5 self-dual two-forms $\hat{B}_{\hat\mu\hat\nu}^{i}$ ($i\in\llbracket1,5\rrbracket$ is the $\SO(5)$ vector index). They lead to two-form potentials $B_{(2)}^{i}$ in 3d, with three-form field strengths dual to purely internal three-form field-strengths $H_{(3)}^{i}$.

  \ce{Should we consider the anti-self dual two-form also?}

  \paragraph{\boldmath $B_{(2)}^{i}$ in $\SO(3,3)_{(2,0)}\times\SO(5)$}
  The coordinates $X^{[MN]}$ of the $\SO(8,4)$ exceptional field theory of ref.~\cite{Hohm:2017wtr} sit in the adjoint $\bm{66}$ of $\SO(8,4)$. Under eq.~\eqref{eq:SO84decomp20}, it decomposes into
  \begin{equation}  
    \bm{66} \longrightarrow (\bm{6},\bm{1}) \oplus (\bm{6},\bm{5}) \oplus (\bm{15},\bm{1}) \oplus (\bm{1},\bm{5}) \oplus (\bm{1},\bm{10}).
  \end{equation}
  Further decomposing $\SO(3,3)_{(2,0)}\times\SO(5)\rightarrow\SL(3)\times\R_{+}\times\SO(5)$, we get
  \begin{equation}
    \begin{aligned}
      \bm{66} &\longrightarrow [(\bm{\bar{3}}_{2},\bm{1})\oplus(\bm{3}_{-2},\bm{1})] \oplus [(\bm{3}_{-2},\bm{5})\oplus(\bm{\bar{3}}_{2},\bm{5})] \oplus [(\bm{3}_{4},\bm{1})\oplus(\bm{1}_{0},\bm{1})\oplus(\bm{8}_{0},\bm{1})\oplus(\bm{\bar{3}}_{-4},\bm{1})] \\
      & \qquad \oplus (\bm{1}_{0},\bm{5}) \oplus (\bm{1}_{0},\bm{10}).
    \end{aligned}
  \end{equation}
  The internal coordinates $y^{m}$ then sit in the representation $(\bm{3}_{4},\bm{1})$ and the two-form potentials $B_{(2)}^{i}$ in $(\bm{3}_{-2},\bm{5})$, they thus originate from the $\SO(3,3)_{(2,0)}\times\SO(5)$ representations $(\bm{15},\bm{1})$ and $(\bm{6},\bm{5})$, respectively.

  \paragraph{\boldmath $H_{(3)}^{i}$ in $\SO(3,3)_{(2,0)}\times\SO(5)$}
  \begin{equation}
    H_{(3)}^{i} \subset(\bm{15},\bm{1})\otimes(\bm{6},\bm{5})=(\bm{6},\bm{5})\oplus(\bm{10},\bm{5})\oplus(\bm{\bar{10}},\bm{5})\oplus(\bm{64},\bm{5}).
  \end{equation}

  \paragraph{\boldmath $H_{(3)}^{i}$ in the embedding tensor}
  The embedding tensor of the $\SO(8,4)$ exceptional theory has two different components: $\theta_{(MN)}\subset\bm{77}$ and $\theta_{[MNPQ]}\subset\bm{495}$. It decomposes as follows under $\SO(8,4)\rightarrow\SO(3,3)_{(2,0)}\times \SO(5)$:
  \begin{equation}
    \begin{aligned}
      \bm{77} &\longrightarrow 2\times(\bm{1},\bm{1}) \oplus (\bm{6},\bm{1}) \oplus {\color{mydarkorange}(\bm{6},\bm{5})} \oplus (\bm{20'},\bm{1}) \oplus (\bm{1},\bm{5}) \oplus (\bm{1},\bm{14}),\\
      \bm{495} &\longrightarrow (\bm{10},\bm{1}) \oplus {\color{mydarkorange}(\bm{10},\bm{5})} \oplus (\bm{\bar{10}},\bm{1}) \oplus {\color{mydarkorange}(\bm{\bar{10}},\bm{5})} \oplus (\bm{15},\bm{1}) \oplus (\bm{1},\bm{5}) \oplus (\bm{1},\bm{10}) \\
      &\qquad\oplus (\bm{6},\bm{10}) \oplus (\bm{6},\bm{\bar{10}}) \oplus (\bm{15},\bm{5}) \oplus (\bm{15},\bm{10}),
    \end{aligned}
  \end{equation}
  where the colored representations are those coming from the three-forms. Only $(\bm{10},\bm{5})$ and $(\bm{\bar{10}},\bm{5})$ feature singlets under the isometry group $\SO(4)\times\SO(4)$. One of these support the $S^{3}$ reduction, while the other can be turned on, leading to new solutions as first demonstrated in ref.~\cite{Hohm:2017wtr,Samtleben:2019zrh}. All singlets sit in $\theta_{MNPQ}$.

 \subsection{\texorpdfstring{${\cal N}=(1,1)$}{N=(1,1)} six-dimensional supergravity}

  \paragraph{6d origin of the three-forms} The ${\cal N}=(1,1)$ supergravity features a two-form $\hat{B}_{\hat\mu\hat\nu}$ Both $\hat{B}_{\hat\mu\hat\nu}$ and its dual lead to two-form potentials in 3d. Their three-form field strengths are dual to purely internal three-form field-strengths $H_{(3)}$ and $*H_{(3)}$, of two-form potentials $C_{(2)}^{1}$ and $C_{(2)}^{2}$.

  \paragraph{\boldmath $C_{(2)}^{1}$ and $C_{(2)}^{2}$in $\SO(4,4)\times\SO(4)$}
  Under $\SO(8,4)\longrightarrow\SO(4,4)\times \SO(4)$, the coordinates $X^{[MN]}$ decompose into
  \begin{equation}  
    \bm{66} \longrightarrow \bm{1}^{(\bm{3},\bm{1})} \oplus \bm{1}^{(\bm{1},\bm{3})} \oplus \bm{8_{\rm v}}^{(\bm{2},\bm{2})} \oplus \bm{28}^{(\bm{1},\bm{1})}.
  \end{equation}
  The internal coordinates and the two-form potentials are singlets under the $\SO(4)$ factor, which is related the 6d vectors only. They thus all belong to the representation $\bm{28}^{(\bm{1},\bm{1})}$.

  \paragraph{\boldmath $H_{(3)}$ and $*H_{(3)}$ in $\SO(4,4)\times\SO(4)$}
  \begin{equation}
    H_{(3)}, *H_{3}\subset\bm{28}^{(\bm{1},\bm{1})}\otimes\bm{28}^{(\bm{1},\bm{1})}=\bm{1}^{(\bm{1},\bm{1})}\oplus\bm{28}^{(\bm{1},\bm{1})}\oplus\bm{35_{\rm v}}^{(\bm{1},\bm{1})}\oplus\bm{35_{\rm s}}^{(\bm{1},\bm{1})}\oplus\bm{35_{\rm c}}^{(\bm{1},\bm{1})}\oplus\bm{300}^{(\bm{1},\bm{1})}\oplus\bm{350}^{(\bm{1},\bm{1})}.
  \end{equation}

  \paragraph{\boldmath $H_{(3)}$ and $*H_{(3)}$ in the embedding tensor}
  \begin{equation}
    \begin{aligned}
      \bm{77} &\longrightarrow {\color{mydarkorange}\bm{1}^{(\bm{1},\bm{1})}} \oplus \bm{1}^{(\bm{3},\bm{3})} \oplus \bm{8_{\rm v}}^{(\bm{2},\bm{2})} \oplus {\color{mydarkorange}\bm{35_{\rm v}}^{(\bm{1},\bm{1})}},\\
      \bm{495} &\longrightarrow {\color{mydarkorange}\bm{1}^{(\bm{1},\bm{1})}} \oplus \bm{8_{\rm v}}^{(\bm{2},\bm{2})} \oplus \bm{28}^{(\bm{1},\bm{3})} \oplus \bm{28}^{(\bm{3},\bm{1})} \oplus {\color{mydarkorange}\bm{35_{\rm s}}^{(\bm{1},\bm{1})}} \oplus {\color{mydarkorange}\bm{35_{\rm c}}^{(\bm{1},\bm{1})}} \oplus \bm{56_{\rm v}}^{(\bm{2},\bm{2})}.
    \end{aligned}
  \end{equation}
  The singlets certainly gauge the trombone symmetry. Each $\bm{35}$ feature $\SO(4)\times\SO(4)$ singlets, but \ce{less clear how to precisely relate to ref.~\cite{Eloy:2021fhc}. Need to consider quadratic constraint?}

@@

\paragraph{\boldmath $H_{(7)}^{\alpha}$ and $H_{(5)}$ in $\SL(8)_{\rm IIB}\times\R_{+}$} Now that we know what are the $\SL(8)_{\rm IIB}\times\R_{+}$ representations corresponding to the internal coordinates, $C_{(6)}^{\alpha}$ and $C_{(4)}$, we can infer those of $H_{(7)}^{\alpha}$ and $H_{(5)}$:
\begin{equation}  \label{eq:H7H5inIIB}
  \begin{aligned}
    H_{(7)}^{\alpha} & \subset \bm{\bar{28}}_{2} \otimes \left(\bm{8}_{3}\oplus\bm{63}_{0}\right) = \bm{\bar{8}}_{5} \oplus \bm{\bar{216}}_{5} \oplus \bm{\bar{28}}_{2} \oplus \bm{\bar{36}}_{2} \oplus \bm{\bar{420}}_{2} \oplus \bm{\bar{1280}}_{2}, \\
    H_{(5)} & \subset \bm{\bar{28}}_{2} \otimes \bm{56}_{1} = \bm{8}_{3} \oplus \bm{216}_{3} \oplus \bm{1344}_{3}.
  \end{aligned}
\end{equation}

@@

\section{Truncations within \texorpdfstring{$\SL(8)_{\rm IIA}\subset\E_{8(8)}$}{SL(8)IIA in E8(8)}}

Can be seen as further reduction of four dimensional $\E_{7(7)}$ solutions on a circle. Under $\E_{8(8)}\rightarrow\E_{7(7)}\times\SL(2)\rightarrow\E_{7(7)}\times\R_{+}$,
\begin{equation}
  \bm{248} \longrightarrow (\bm{1},\bm{3}) \oplus (\bm{56},\bm{2}) \oplus (\bm{133},\bm{3})\longrightarrow \bm{1}_{2} \oplus \bm{56}_{1} \oplus \bm{1}_{0} \oplus \bm{133}_{0} \oplus \bm{56}_{-1} \oplus \bm{1}_{-2}.
\end{equation}
The $\E_{7(7)}$ coordinates are in the $\bm{56}_{1}$, and $C_{(6)}$ in $\bm{56}_{-1}$ (11d $\hat{C}_{\hat\mu\hat\nu\hat\rho}$ leads to $C_{\mu\nu\,m}$ in 3d, $H_{\mu\nu\rho\,m}$ dual to purely internal $H_{(7)}$ of potential $C_{(6)}$). Then,
\begin{equation}
    H_{(7)} \subset \bm{56}_{1} \otimes \bm{56}_{-1} = \bm{1}_{0} \oplus \bm{133}_{0} \oplus \bm{1463}_{0} \oplus \bm{1539}_{0}.
\end{equation}
Under $\E_{8(8)}\rightarrow\E_{7(7)}\times\SL(2)\rightarrow\E_{7(7)}\times\R_{+}$, the $\E_{8(8)}$ embedding tensor decomposes as
\begin{equation}
    \bm{3875} \longrightarrow \bm{133}_{2} \oplus \bm{56}_{1} \oplus \bm{912}_{1} \oplus {\color{mydarkorange}\bm{1}_{0}} \oplus {\color{mydarkorange}\bm{133}_{0}} \oplus {\color{mydarkorange}\bm{1539}_{0}} \oplus \bm{56}_{-1} \oplus \bm{912}_{-1} \oplus \bm{133}_{-2}.
\end{equation}

\paragraph{\boldmath $\SO(8)_{\rm IIA}$ singlets}
Under $\E_{7(7)}\rightarrow\SL(8)_{\rm IIA}$:
\begin{equation}
  \begin{aligned}
    \bm{133} & \longrightarrow \bm{63} \oplus \bm{70},\\
    \bm{1539} & \longrightarrow \bm{63} \oplus \bm{378} \oplus \bm{\bar{378}} \oplus \bm{720}.
  \end{aligned}
\end{equation}
No singlet other that $\bm{1}$.

\paragraph{\boldmath $\SO(7)$ singlets}
Under $\E_{7(7)}\rightarrow\SL(7)\times\R_{+}$:
\begin{equation}
  \begin{aligned}
    \bm{133} & \longrightarrow \bm{1}_{0} \oplus \ldots,\\
    \bm{1539} & \longrightarrow \bm{1}_{0} \oplus \ldots
  \end{aligned}
\end{equation}
where only representations featuring $\SO(7)$ singlets have been specified.

\paragraph{\boldmath $\SO(6)\times\R_{+}$ singlets}
Under $\E_{7(7)}\rightarrow\SL(6)\times\SL(2)\times\R_{+}$:
\begin{equation}
  \begin{aligned}
    \bm{133} & \longrightarrow (\bm{1},\bm{1})_{0} \oplus \ldots,\\
    \bm{1539} & \longrightarrow 2\times(\bm{1},\bm{1})_{0} \oplus \ldots\\
  \end{aligned}
\end{equation}
where only representations featuring $\SO(6)\times\R_{+}$ singlets have been specified.

\paragraph{\boldmath $\SO(5)\times\SO(3)$ singlets}
Under $\E_{7(7)}\rightarrow\SL(5)\times\SL(3)\times\R_{+}$:
\begin{equation}
  \begin{aligned}
    \bm{133} & \longrightarrow (\bm{1},\bm{1})_{0} \oplus \ldots,\\
    \bm{1539} & \longrightarrow 2\times(\bm{1},\bm{1})_{0} \oplus \ldots\\
  \end{aligned}
\end{equation}
where only representations featuring $\SO(5)\times\SO(3)$ singlets have been specified.

\paragraph{\boldmath $\SO(4)\times\SO(4)$ singlets}
Under $\E_{7(7)}\rightarrow\SL(4)\times\SL(4)\times\R_{+}$:
\begin{equation}
  \begin{aligned}
    \bm{133} & \longrightarrow (\bm{1},\bm{1})_{0} \oplus (\bm{1},\bm{1})_{4} \oplus (\bm{1},\bm{1})_{-4} \oplus \ldots,\\
    \bm{1539} & \longrightarrow 2\times(\bm{1},\bm{1})_{0} \oplus \ldots\\
  \end{aligned}
\end{equation}
where only representations featuring $\SO(4)\times\SO(4)$ singlets have been specified.

\paragraph*{} The singlets always come from the $\bm{63}$ and $\bm{720}$ of $\SL(8)_{\rm IIB}$ (and $\bm{70}$ for $\SL(4)\times\SL(4)\times\R_{+}$).

\appendix

\section{Miniminal ${\cal N}=(1,0)$ six-dimensional supergravity}
We consider reductions within the minimal ${\cal N}=(1,0)$ six-dimensional supergravity, leading to duality group $\SO(4,4)$ in three dimensions, from which the half-maximal cases ${\cal N}=(1,1)$ and ${\cal N}=(2,0)$ can be deduced (in those cases the duality group in three dimensions in $\SO(8,4)$).

The coordinates $X^{[MN]}$ of the $\SO(p,q)$ exceptional field theory of ref.~\cite{Hohm:2017wtr} sit in the adjoint $\bm{28}$ of $\SO(4,4)$. Under $\SO(4,4)\rightarrow\SO(3,3)\times\R_{+}$, it decomposes into
\begin{equation}  
  \begin{aligned}
    \bm{28} &\longrightarrow \bm{6}_{2} \oplus \bm{1}_{0} \oplus \bm{15}_{0} \oplus \bm{6}_{-2},\\
    X^{MN} &\longrightarrow \{Y^{A0},Y^{0}{}_{0},Y^{[AB]},Y^{A}{}_{0}\}.
  \end{aligned}
\end{equation}
Further decomposing $\SO(4,4)\rightarrow\SO(3,3)\times\R_{+}\rightarrow\SL(3)\times\R_{+}\times\R_{+}$, we get
\begin{equation}  \label{eq:decomp28SO8}
  \bm{28} \longrightarrow \left[\bm{\bar{3}}_{2,2} \oplus \bm{3}_{-2,2}\right] \oplus \bm{1}_{0,0} \oplus \left[\bm{3}_{4,0} \oplus \bm{1}_{0,0} \oplus \bm{8}_{0,0} \oplus \bm{\bar{3}}_{-4,0}\right] \oplus \left[\bm{\bar{3}}_{2,-2} \oplus \bm{3}_{-2,-2}\right].
\end{equation}
They are two physically different possibilities to embed the internal coordinates in $X^{MN}$, corresponding to the two different half-maximal supergravities in six dimensions:\footnote{The choices are equivalent in $\SO(4,4)$ (through triality), but different once embedded in $\SO(8,4)$.}
\begin{equation}  \label{eq:coordSO8}
  \begin{aligned}
    {\cal N}=(1,1):&\qquad y^{m}=Y^{m0}\subset\bm{\bar{3}}_{2,2} \longleftarrow \bm{6}_{2},\\
    {\cal N}=(2,0):&\qquad \tilde{y}_{m}=\varepsilon_{mnp}Y^{np}\subset\bm{3}_{4,0}\longleftarrow\bm{15}_{0}.
  \end{aligned}
\end{equation}

\paragraph{6d origin of the three-forms} The ${\cal N}=(1,0)$ supergravity features a two-form $\hat{B}_{\hat\mu\hat\nu}$. Both $\hat{B}_{\hat\mu\hat\nu}$ and its dual lead to two-form potentials in 3d. Their three-form field strengths are dual to purely internal three-form field-strengths $H_{(3)}$ and $*H_{(3)}$, of two-form potentials $C_{(2)}^{1}$ and $C_{(2)}^{2}$.

\paragraph{\boldmath $C_{(2)}^{1}$ and $C_{(2)}^{2}$ in $\SO(3,3)\times\R_{+}$} Given the decomposition~\eqref{eq:decomp28SO8} and the coordinates~\eqref{eq:coordSO8}, the two forms sit in the following representations:
\begin{equation}
  \begin{aligned}
    {\cal N}=(1,1):&\qquad C^{1}_{(2)}\subset\bm{\bar{3}}_{-4,0} \longleftarrow\bm{15}_{0}\quad{\rm and}\quad C^{2}_{(2)}\subset\bm{3}_{4,0} \longleftarrow\bm{15}_{0},\\
    {\cal N}=(2,0):&\qquad C^{1}_{(2)}\subset\bm{3}_{-2,2} \longleftarrow\bm{6}_{2}\quad{\rm and}\quad C^{2}_{(2)}\subset\bm{\bar{3}}_{2,2} \longleftarrow\bm{6}_{2}.
  \end{aligned}
\end{equation}

\paragraph{\boldmath $H_{(3)}$ and $*H_{(3)}$ in $\SO(3,3)\times\R_{+}$}
\begin{equation}
  \begin{aligned}
    {\cal N}=(1,1):&\qquad H_{(3)},*H_{(3)} \subset\bm{6}_{2}\otimes\bm{15}_{0}=\bm{6}_{2}\oplus\bm{10}_{2}\oplus\bm{\bar{10}}_{2}\oplus\bm{64}_{2},\\
    {\cal N}=(2,0):&\qquad H_{(7)},*H_{(7)} \subset\bm{10}_{0}\otimes\bm{6}_{2}=\bm{6}_{2}\oplus\bm{10}_{2}\oplus\bm{\bar{10}}_{2}\oplus\bm{64}_{2},
  \end{aligned}
\end{equation}

\paragraph{\boldmath $H_{(3)}$ and $*H_{(3)}$ in the embedding tensor} The embedding tensor of the $\SO(4,4)$ exceptional theory has two different components: $\theta_{[MNPQ]}\subset\bm{35_{\rm s}}\oplus\bm{35_{\rm c}}$ and $\theta_{(MN)}\subset\bm{35_{\rm v}}$. It decomposes as follows under $\SO(4,4)\rightarrow\SO(3,3)\times\R_{+}$:
\begin{equation}
  \begin{aligned}
    \bm{35_{\rm v}} &\longrightarrow \bm{1}_{4} \oplus {\color{mydarkorange}\bm{6}_{2}} \oplus \bm{1}_{0} \oplus \bm{20'}_{0} \oplus \bm{6}_{-2} \oplus \bm{1}_{-4},\\
    \bm{35_{\rm s}} &\longrightarrow {\color{mydarkorange}\bm{10}_{2}} \oplus \bm{15}_{0}  \oplus \bm{\bar{10}}_{-2},\\
    \bm{35_{\rm c}} &\longrightarrow {\color{mydarkorange}\bm{\bar{10}}_{2}} \oplus \bm{15}_{0}  \oplus \bm{10}_{-2},
  \end{aligned}
\end{equation}
where the colored representations are those coming from the three-forms. Only $\bm{10}_{2}$ and $\bm{\bar{10}}_{2}$ feature $\SO(4)$ singlets. \ce{So no distinction between (1,1) and (2,0)? Because triality, or I made errors?}
